Scalar and Representative Observables for Polarimetric SAR Data

### 2014-02-11 paper_dev/article.tex
added reference to KS test

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
While a good p-value does not mean automatic acceptance of the model,
  consistently high p-value readings suggest that the proposed model should not be ignored.

>>>>

Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
Again, although the histogram is much tighter, the match is visually obvious in all cases.
This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov–Smirnov goodness-of-fit test.
While a good p-value does not mean automatic acceptance of the model,
  consistently high p-value readings suggest that the proposed model has excellent confidence-limit \cite{Kolmogoroff_1941_AMS_461}.
